Polynomial Chaos for the Estimation of Manning's Friction

### 2013-12-16 paper/tsunami.tex
some edits to tsnunami section and adding authors

\subsubsection{Observations}

The observations used in this study are from the Deep-ocean Assessment and Reporting of Tsunamis (DART) buoy system developed and maintained by the National Oceanic and Atmospheric Administration (NOAA).  The purpose of the network is to provide early-warning detection and forecasting of tsunami propagation in the Pacific Ocean \alert{need citation for this?}.  The DART buoys closest to the earthquake source of the \tohoku tsunami were buoys 21418, 21413, 21401, and 21419 whose locations are shown in Figure~\ref{fig:setup} and whose de-tided data for the event are show in Figure~\ref{fig:obs}.

% \begin{figure}[tb]    
%     \centering
%     \begin{subfigure}[b]{0.48\textwidth}
%         \includegraphics[width=\textwidth]{./figures/DART_locations}
%         \caption{}
%         \label{fig:dart_locations}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.48\textwidth}
%         \includegraphics[width=\textwidth]{./figures/DART_data}
%         \caption{}
%         \label{fig:dart_data}
%     \end{subfigure}
%     \caption{Stuff}
%   \end{figure}

@@

\subsubsection{Bathymetry}

\subsection{Parametric Uncertainty}
To represent the uncertainty in the Manning's $n$ coefficients a uniform distribution was assumed as the prior where $n$ was sampled in the interval $[0.005-0.2]$.  The regions

Uniform distribution is assumed as the prior for the three manning coefficients.
such that UN = [0.005-0.2]. The three regions are shown in Figure~\ref{fig:setup}(right)

>>>>

@@

\subsubsection{Bathymetry}
The bathymetry is shown in Figure~\ref{fig:setup} in addition to the topography
of the Pacific Ocean.
\subsubsection{Observations}

The observations used in this study are from the Deep-ocean Assessment and Reporting of Tsunamis (DART) buoy system developed and maintained by the National Oceanic and Atmospheric Administration (NOAA).  The purpose of the network is to provide early-warning detection and forecasting of tsunami propagation in the Pacific Ocean \alert{need citation for this?}.  The DART buoys closest to the earthquake source of the \tohoku tsunami were buoys 21418, 21413, 21401, and 21419 whose locations are shown in Figure~\ref{fig:setup}(left) and whose de-tided data for the event are shown in Figure~\ref{fig:setup}(right).
\subsection{Parametric Uncertainty}
In this work, we seek to quantify parametric uncertainty namely due 
to the uncertainty in the roughness parameter $n$. To this end,
we characterize the roughness $N$ by three different parameters
that are varied in three different regions but are assume
constant in each region. The three regions are as follows: 
on-shore who coefficnet is denoted by $N_1$, near-shore 
denoted by $N_2$, and deep-water denoted by $N_3$.
The three regions are shown in Figure~\ref{fig:ceofs}.
To carry out the uncertainty quantification we have employed polynomial chaos expansions 
as used in \cite{sraj:2013a,sraj:2013b}. The method and its application
to our problem is described in Section~\ref{sec:uqpce}.  
To represent the uncertainty in the Manning's $n$ coefficients a uniform distribution was assumed as the prior where $n$ was sampled in the interval $[0.005-0.2]$.
